Online Classification of arXiv Papers Based on Your Preferences

### 2014-05-13 Paper.tex
more paper updates

\begin{document}
\title{Online Learning Your arXiv Preferences}
\author{Steve Delong and Joey McDonald}
\maketitle
\begin{abstract}
Our goal was to construct a tool that feeds a user a selection of abstracts of papers from the online database, arXiv.org, recieves a label indicating whether the user is interested in that article or not, and progressively learns the users preferences through an online learning algorithm. It uses this information to present articles that it believes the user will like. We created and tested this using a few sample users' preferences including each of ours. Beyond constructing the tool we found some theoretical justification for bounding the number of updates in expectation while only presenting a fraction of samples that are predicted to be uninteresting.
\end{abstract}

@@

One of the most important aspects of this tool is the feature data itself, and what characteristics distinguish

>>>>

\begin{document}
\title{Online Classification of arXiv Papers Based on Your Preferences}
\author{Steve Delong and Joey McDonald}
\maketitle
\begin{abstract}
Our goal was to construct a tool that feeds a user a selection of abstracts of papers from the online database, arXiv.org, recieves a label indicating whether the user is interested in that article or not, and progressively learns the users preferences through an online learning algorithm. It uses this information to present articles that it believes the user will like. We created and tested this using a few sample users' preferences including each of ours. Beyond constructing the tool we found some theoretical justification for bounding the number of updates in expectation while only presenting a fraction of samples that are predicted to be uninteresting.
\end{abstract}

@@

An important feature of any text classification device is the data used to construct feature vectors. There are several approaches to text classification, itself a large field of research. We take an elementary approach and use a bag-of-words model, that is, performing a word count for each distinct word in the abstract and converting that into a vector. 
Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in {\tt ArxivData.py} and called when

%One of the most important aspects of this tool is what is used for feature data. There are several approaches to text categorization that
